\documentclass{article}
\usepackage{amsmath}

\title{Chinglish Test Sample}
\author{Test Author}

\begin{document}

\maketitle

\section{Introduction}

In recent years, deep learning can achieve state-of-the-art results in many research field.
According to previous work, the model can learn knowledge from data.
Result shows that our method can get good performance on several benchmark.

\section{Method}

We make the model to learn representations through self-supervised learning.
Different with prior work, our approach is based from transformer architecture.
The function makes the error reduce significantly.
We try to explore the relationship between loss and accuracy.

\section{Experiments}

In experiment, we found that our method works well on ImageNet dataset.
The results demonstrates that the proposed method is more and more important
for computer vision applications. So we believe this is a big contribution.

Most of methods cannot achieve similar with our performance.
We should notice that the model have several advantage over baselines.

\section{Tense Issues}

Smith et al. \cite{smith2023} propose a new method that significantly improves
accuracy. The authors evaluates their approach on CIFAR-10 and achieves 95\% accuracy.
We adopt their framework and extend it to video understanding.

\section{Structural Issues}

First, we introduce the problem. Second, we describe the method. Third, we show results.
Fourth, we discuss implications. Fifth, we conclude.

In summary, we have done the following things: we proposed a method, we conducted experiments,
and we analyzed the results.

\end{document}
